Posterior summarisation in Bayesian phylogenetics using Tracer 1.7

### 2018-02-10 manuscript/syst_biol/tracer17_systbiol.tex
small tweaks

\abstract{
Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) plays a central role in understanding evolutionary history from molecular sequence data.
Visualising and analysing the MCMC-generated samples from the posterior distribution is a key step in any non-trivial Bayesian inference. 
We present the software package \tracer\ (version 1.7) for visualising and analysing the MCMC trace files generated through Bayesian phylogenetic inference.
\tracer\ provides kernel density estimation, multivariate visualisation, demographic trajectory reconstruction, conditional posterior distribution summary and more.
\tracer\ is open-source and available at \url{http://beast.community/tracer}.
[Bayesian inference; phylogenetics; Markov chain Monte Carlo.]
\vspace*{-25pt}
}

@@

\subsection*{Dynamics of rabies across North American bats}

@@

Phylogeographic BSSVS inference includes parameters of both integer (number of non-zero transition rates) and categorical (host or location-state) trace types.
%While a single parameter of such types can easily be visualised using a frequency plot,
In \tracer, a bubble chart visualises the joint probability distribution between two integer or categorical traces (see Figure \ref{fig:4tabs}a).
Circle area is proportional to the joint probability, %the blue coloured circle is in the credible set of given a probability threshold default to 0.95, the red is in the set not in the credible set.
with a coloured tile background if this probability reaches a nominal threshold to enhance visibility.
%The coloured background can also help to show the area of the credible set and non-credible set.
%Multiple integer parameters can also be visualised using
Marginal density plots can also display multiple integer parameters, each with unique colour scales (see Figure \ref{fig:4tabs}b).
With approximately equal numbers of transition rates, both figures suggest similar host and location trait model complexity.
%Both figures show a clear overlap in the number of non-zero transition rates in the discrete trait models for host and location, as identified using a BSSVS procedure.
\tracer\ also provides
%The visualisation options for integer or categorical parameters are complemented with
 popular visualisations for continuous parameters, including scatter plots for two parameters (see Figure \ref{fig:4tabs}c),
 and extensions for correlations between $\ge\hspace{-0.32em}2$ continuous parameters (Figure \ref{fig:4tabs}d; \citet{Murdoch}).
 %, which indicates a strong positive correlation between the clock rates of both discrete trait models.
%We also provide an extension of such a scatter plot for multiple (i.e. more than two) continuous variables (see Figure \ref{fig:4tabs}d; \citet{Murdoch}), which makes use of coloured ellipses to indicate the strength of correlation between each pair of continuous variables.
Colour gradients indicate strength and direction of the correlation, from red (strong negative) to blue (strong positive).
%with a colour gradient from white to dark blue indicating increasingly strong correlation and a colour gradient from white to dark red indicating increasingly strong anti-correlation.
Ellipse shapes re-enforce the strength of correlation, with no correlation appearing as a circle and perfect (anti-)correlation as a line.
%Finally, in order to display the joint marginal distribution between a continuous variable and an integer or categorical variable, we make use of box-and-whisker plots.
%Using such a plot (Figure \ref{fig:4tabs}e), we can infer that the range of the non-zero transition rates can depend on the ancestral location state inferred at the root of the underlying phylogeny.

>>>>

\abstract{
Bayesian inference of phylogeny using Markov chain Monte Carlo (MCMC) plays a central role in understanding evolutionary history from molecular sequence data.
Visualising and analysing the MCMC-generated samples from the posterior distribution is a key step in any non-trivial Bayesian inference. 
We present the software package \tracer\ (version 1.7) for visualising and analysing the MCMC trace files generated through Bayesian phylogenetic inference.
\tracer\ provides kernel density estimation, multivariate visualisation, demographic trajectory reconstruction, conditional posterior distribution summary and more.
\tracer\ is open-source and available at \url{http://beast.community/tracer}.
[Bayesian inference; phylogenetics; Markov chain Monte Carlo; visualisation]
\vspace*{-25pt}
}

@@

\subsection*{Cross-species dynamics of North American bat rabies}

@@

Phylogeographic BSSVS inference includes parameters of both integer (number of non-zero transition rates) and categorical (host or location-state) trace types.
%While a single parameter of such types can easily be visualised using a frequency plot,
In \tracer, a bubble chart visualises the joint probability distribution between two integer or categorical traces (see Figure \ref{fig:4tabs}a).
Circle area is proportional to the joint probability, %the blue coloured circle is in the credible set of given a probability threshold default to 0.95, the red is in the set not in the credible set.
with a coloured tile background if this probability reaches a nominal threshold to enhance visibility.
%The coloured background can also help to show the area of the credible set and non-credible set.
%Multiple integer parameters can also be visualised using
Marginal density plots can also display multiple integer parameters, each with unique colour scales (see Figure \ref{fig:4tabs}b).
With approximately equal numbers of transition rates, both figures suggest similar host and location trait model complexity.
%Both figures show a clear overlap in the number of non-zero transition rates in the discrete trait models for host and location, as identified using a BSSVS procedure.
\tracer\ also provides
%The visualisation options for integer or categorical parameters are complemented with
 popular visualisations for continuous parameters, including scatter plots for two parameters (see Figure \ref{fig:4tabs}c),
 and extensions for correlations between $\ge\hspace{-0.08em}2$ continuous parameters (Figure \ref{fig:4tabs}d; \citet{Murdoch}).
 %, which indicates a strong positive correlation between the clock rates of both discrete trait models.
%We also provide an extension of such a scatter plot for multiple (i.e. more than two) continuous variables (see Figure \ref{fig:4tabs}d; \citet{Murdoch}), which makes use of coloured ellipses to indicate the strength of correlation between each pair of continuous variables.
Colour gradients indicate strength and direction of the correlation, from red (strong negative) to blue (strong positive).
%with a colour gradient from white to dark blue indicating increasingly strong correlation and a colour gradient from white to dark red indicating increasingly strong anti-correlation.
Ellipse shapes re-enforce the strength of correlation, with no correlation appearing as a circle and perfect (anti-)correlation as a line.
%Finally, in order to display the joint marginal distribution between a continuous variable and an integer or categorical variable, we make use of box-and-whisker plots.
%Using such a plot (Figure \ref{fig:4tabs}e), we can infer that the range of the non-zero transition rates can depend on the ancestral location state inferred at the root of the underlying phylogeny.
